---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hubspot

> Access Hubspot CRM data in R

<!-- badges: start -->
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Travis build status](https://travis-ci.org/lockedata/hubspot.svg?branch=master)](https://travis-ci.org/lockedata/hubspot)
 [![Locke Data Slack](https://img.shields.io/badge/Slack-discuss-blue.svg?logo=slack&longCache=true&style=flat)](https://join.slack.com/t/lockedata/shared_invite/enQtMjkwNjY3ODkwMzg2LTI1OGU1NTM3ZGIyZGFiNTdlODI3MzU2N2ZlNDczMjM4M2U2OWVmNDMzZTQ1ZGNlZDQ3MGM2MGVjMjI2MWIyMjI)
[![Codecov test coverage](https://codecov.io/gh/lockedata/hubspot/branch/master/graph/badge.svg)](https://codecov.io/gh/lockedata/hubspot?branch=master)
<!-- badges: end -->

The goal of `hubspot` is to enable access to [Hubspot CRM](//hubspot.com) data. It uses the [Hubspot API](developers.hubspot.com/docs/overview).

All functions are named following a `hs_<endpointname>_raw()`/`hs_<endpointname>_tidy()`, with `hs_<endpointname>_tidy()` offering at least one view: e.g. get a nested list of deals data with `hs_deals_raw()` and transform it to a tibble of associations, properties history, properties or stages history using `hs_deals_tidy()`. 

Refer to the [online reference](https://itsalocke.com/hubspot/reference) to see what endpoints are supported at the moment. Feel free to suggest new "getters" (`hs_<endpointname>_raw()`) and tidier options (`view` of `hs_<endpointname>_tidy()`) in the [issue tracker](https://github.com/lockedata/hubspot/issues).

## Example

```{r example}
library("hubspot")

deal_props <- hs_deal_properties_tidy()
head(deal_props)

deals <- hs_deals_raw(properties = deal_props, max_iter = 1)
str(deals)

deal_stages <- hs_deals_tidy(deals, view = "properties")
deal_stages
```


## Installation

```{r eval=FALSE}
remotes::install_github("lockedata/hubspot")
```


```{r child='man/rmdhunks/auth.Rmd'} 
```

Find more details on each method [in the vignette about authorization](https://itsalocke.com/hubspot/articles/auth).

## Contributions welcome!

Wanna report a bug or suggest a feature? Great stuff! For more information on how to contribute check out [our contributing guide](.github/CONTRIBUTING.md).

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
