---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hubspot

> Access Hubspot CRM data in R

<!-- badges: start -->
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Travis build status](https://travis-ci.org/lockedata/hubspot.svg?branch=master)](https://travis-ci.org/lockedata/hubspot)
 [![Locke Data Slack](https://img.shields.io/badge/Slack-discuss-blue.svg?logo=slack&longCache=true&style=flat)](https://join.slack.com/t/lockedata/shared_invite/enQtMjkwNjY3ODkwMzg2LTI1OGU1NTM3ZGIyZGFiNTdlODI3MzU2N2ZlNDczMjM4M2U2OWVmNDMzZTQ1ZGNlZDQ3MGM2MGVjMjI2MWIyMjI)
<!-- badges: end -->

The goal of `hubspot` is to enable access to [Hubspot CRM](//hubspot.com) data. It uses the [Hubspot API](developers.hubspot.com/docs/overview).

## Example

```{r example}
library(hubspot)

deal_props <- get_deal_properties("demo")
deal_props

deals <- get_deals("demo", properties = deal_props, max_iter = 1)
deals
```


## Installation

```{r eval=FALSE}
remotes::install_github("lockedata/hubspot")
```

## Authentication

### API key

The API key should be set using the `hubspot_key_set()` function, that relies on the `keyring` package that stores the key in the system default credential store (see `keyring` docs).

```r
# Either input the key as parameter
hubspot_key_set("yourapikey")

# Or just call the function,
# the key will be asked interactively
hubspot_key_set()
```

If no API key is set, the "demo" key is used and a message is printed to the screen.

You can check the daily usage related to the API key via `hubspot_api_usage()`. Calls in the package are rate limited (100 requests every 10 seconds) but there's also a daily limit on calls.

```{r usage}
hubspot_api_usage()
```

## Contributions welcome!

Wanna report a bug or suggest a feature? Great stuff! For more information on how to contribute check out [our contributing guide](.github/CONTRIBUTING.md).

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
